---
title: "DeepBlue-R"
author: "Felipe Albrecht"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_of_sections: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

DeepBlue Epigenomic Data Server is a tool that allows researchers to access epigenomic data from different consortia.
DeepBlue provides extensive documentation: [API Reference](http://deepblue.mpi-inf.mpg.de/api.php), [examples](http://deepblue.mpi-inf.mpg.de/examples.php), [use cases](http://deepblue.mpi-inf.mpg.de/use_cases.php), and a [complete users' manual](http://deepblue.mpi-inf.mpg.de/manual). With exception of the API listing, that is language agnostic, the others documentation focus on the python language. This document will present how to access DeepBlue by its R package.

# Getting started
## Installation
For installing DeepBlue R package, simply execute:

Automatic installation of DeepBlue-R and its companion data packages can be performed using the devtools package. All you have to do is to execute the
following command in your R environment:

```{r, echo=FALSE}
#library(devtools)
#install_github("MPIIComputationalEpigenetics/DeepBlue-R")
```

You can test your installation executing:
```{r, echo=FALSE}
#deepblue.info("me")
```

## Overview of the DeepBlue commands

DeepBlue provides a comprehensive programmatic interface for finding, selecting, filtering, summarizing and downloading region sets.
A list of all commands available by DeepBlue is provided in its [API page](http://deepblue.mpi-inf.mpg.de/api.php).

For reference, following are listed the most used DeepBlue commands:

| Category        | Command               | Description                           |
|-----------------|-----------------------|---------------------------------------|
| Information     | info                  | Obtain information about an entity    |
| List and search | list genomes          | List all registered genomes           |
|                 | list biosources       | List all registered biosources        |
|                 | list samples          | List all registered samples           |
|                 | list epigenetic marks | List all registered epigenetic marks  |
|                 | list experiments      | List all available experiments        |
|                 | list annotations      | List all available annotations        |
|                 | search                | Perform a full-text search            |
| Selection       | select regions        | Select regions from experiments       |
|                 | select experiments    | Select regions from experiments       |
|                 | select annotations    | Select regions from annotations       |
|                 | select genes          | Select genes as regions               |
|                 | tiling regions        | Generate tiling regions               |
|                 | input regions         | Upload and use a small region-set     |
| Operation       | aggregate             | Aggregate and summarize regions       |
|                 | filter regions        | Filter regions using their attributes |
|                 | flank                 | Generate flanking regions             |
|                 | intersection          | Filter overlapping regions            |
|                 | merge queries         | Merge two regions set                 |
| Result          | count regions         | Count selected regions                |
|                 | score matrix          | Request a score matrix                |
|                 | get regions           | Request the selected regions          |
| Request         | get request data      | Obtain the requested data             |


This package provides a set of functions for facilitate the API usage:

| Category        | Command               | Description                                       |
|-----------------|-----------------------|---------------------------------------------------|
| Request         | batch_export_results  | Download the data a set of requests               |
|                 | process_request       | Wait for a request be processed                   |
|                 | get_request_data      | Download and convert the requested data           |



# DeepBlue usage

The usual DeepBlue usage starts with a listing command. For example, listing all biosources:

### EXAMPLE.

It is also possible to list all epigenetic marks:

#### EXAMPLE