---
title: "DeepBlue Epigenomic Data Server - R"
author: "Felipe Albrecht"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

DeepBlue Epigenomic Data Server is a tool that allows researchers to access epigenomic data from different consortia.
DeepBlue provides extensive documentation: [API Reference](http://deepblue.mpi-inf.mpg.de/api.php), [examples](http://deepblue.mpi-inf.mpg.de/examples.php), [use cases](http://deepblue.mpi-inf.mpg.de/use_cases.php), and a [complete users' manual](http://deepblue.mpi-inf.mpg.de/manual). With exception of the API listing, that is language agnostic, the others documentation focus on the python language. This document will present how to access DeepBlue by its R package.


## Installation
For installing DeepBlue R package, simply execute:

```{r}
library(devtools)
install_github("MPIIComputationalEpigenetics/DeepBlue-R")
```

You can test your installation executing:
```{r}
#deepblue.info("me")
```

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output:
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
